Distance Sampling in \proglang{R}

### 2015-12-07 paper.Rmd
binned distances

>>>>

It is also possible to use distances collected in intervals ("binned", as opposed to "exact" distance data) to model the detection function. In this case a set of cutpoints for the bins must be provided rather than the \code{distance} column, these are specified as two columns \code{distbegin} and \code{distend}.
